### 2019-02-14 sections/intuition.tex
Changes to text section 3.3

\fixme{Extend}
Tasks process input events from users.
Sensors are also regarded as users.
Gives rise to communication with the environment.

In \TOPHAT, communication with the environment is represented by editors.
A task of the form $\Edit v$, where $v$ is of type $\tau$, can receive any change event with a value of type $\tau$ and additionally the special event $\Empty$ that empties the editor.
There are no output events, instead the environment can always inspect a task's value.
% However, the environment can always inspect the current value of an editor.

Editors have no notion of continuation.
Their sole purpose is to interact with the environment, retaining the last value that has been sent to them.
%
They can be used for both input and output.
The interpretation of whether an editor represents input or output is left to the reader.
An empty editor is most commonly interpreted as a prompt to input data, while a filled editor can be seen either as outputting its value, or as an input that comes with a default value.

\begin{example}[Vending machine]

% The following \CSP program models a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins. \todo{remove CSP?}
% \begin{equation*}
%   \textit{coin} \to (\textit{small} \to \text{STOP} \mid \textit{coin} \to \textit{large} \to \text{STOP})
% \end{equation*}
% % An equivalent reactive system in \ESTEREL could be defined as\fixme{validate}
% % \begin{equation*}
%   % V_\text{\ESTEREL} = \text{await } \textit{coin}; ( \text{await } \textit{button}; \text{emit } \textit{small} \parallel \text{await } \textit{coin}; \text{await } \textit{button}; \text{emit } \textit{large})
% % \end{equation*}
% A vending machine in \TOPHAT that is close in spirit to the one above looks as follows.

This example demonstrates external communication and choice.
A vending machine in \TOPHAT that dispenses a small biscuit for one coin and a large biscuit for two coins can be specified as follows
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small" else if n == 2 then edit "large" else fail
\end{TASK}
The task asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money.

>>>>

The evaluation of tasks is driven by input events from users. When the system
receives a valid event, it is applied to the current task, which results in a
new task. This gives rise to communication with the users of the system.

In \TOPHAT, this communication with the environment is represented by editors,
which are denoted by a box symbol.
A task of the form $\Edit v$, where $v$ is of type $\tau$, can receive a change
event with a value of type $\tau$ and additionally the special event $\Empty$
that empties the editor.
There are no external output events, instead the new task can be observed, as
described in the next section.
% However, the environment can always inspect the current value of an editor.

Editors have no notion of continuation. Their sole purpose is to facilitate
interact with the user, retaining the last value that has been sent to them.
%
Since editors can be observed in for example a user interface, they can be used
for both input and output. An empty editor is most commonly interpreted as a
prompt to input data, while a filled editor can be seen either as outputting its
value, or as an input that comes with a default or current value.

\begin{example}[Vending machine]
\label{Vending machine}
% The following \CSP program models a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins. \todo{remove CSP?}
% \begin{equation*}
%   \textit{coin} \to (\textit{small} \to \text{STOP} \mid \textit{coin} \to \textit{large} \to \text{STOP})
% \end{equation*}
% % An equivalent reactive system in \ESTEREL could be defined as\fixme{validate}
% % \begin{equation*}
%   % V_\text{\ESTEREL} = \text{await } \textit{coin}; ( \text{await } \textit{button}; \text{emit } \textit{small} \parallel \text{await } \textit{coin}; \text{await } \textit{button}; \text{emit } \textit{large})
% % \end{equation*}
% A vending machine in \TOPHAT that is close in spirit to the one above looks as follows.

This example demonstrates external communication and choice.
A vending machine in \TOPHAT that dispenses a small biscuit for one coin and a large biscuit for two coins can be specified as follows
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small"
                                                       else if n == 2 then edit "large"
                                                                      else fail
\end{TASK}
The task asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the right hand side of the step combinator results in $\Fail$.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money.
